
\documentclass[10pt]{article}

\usepackage[margin=0.8in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[hidelinks]{hyperref}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.6em}

\begin{document}

\textbf{SHIVAM SHARMA}\\
Tempe, AZ $\cdot$ +1 (480) 208 -5286 $\cdot$ \href{mailto:sshar443@asu.edu}{sshar443@asu.edu}\\
GitHub: \href{https://github.com/shivam15112003}{github.com/shivam15112003} $\cdot$ LinkedIn: \href{https://www.linkedin.com/in/ss1511/}{www.linkedin.com/in/ss1511}\\
Portfolio: \href{https://shivam15112003.github.io/shivam-portfolio/}{shivam15112003.github.io/shivam-portfolio}\\[0.5em]

December 20, 2025\\[0.5em]

Hiring Manager\
Demeter Roboti\\
Glendale, CA\\[0.5em]

Dear Hiring Manager,\\

I am writing to express my profound interest in the Head of Research And Development position at Demeter Robotics, as advertised. With a strong foundation in robotics and autonomous systems, coupled with practical experience in AI/ML engineering, I am eager to contribute to your mission of addressing critical labor shortages in agriculture through innovative robotic solutions. My expertise in architecting complex robotic frameworks, designing real-time systems, and integrating learning methods aligns perfectly with the technical leadership and hands-on execution required for this role.

My background includes extensive work with ROS2, C++, and Python, which are foundational to architecting and implementing robust robot stacks and custom nodes for real-world deployments. Projects such as developing an agentic AI pipeline for prompt-to-action robot control, where I integrated monocular depth estimation and robust safety checks, demonstrate my ability to bridge perception, planning, and execution. Furthermore, my experience at Salesforce involved shipping real-time multi-attribute face analytics and developing a driver drowsiness system, both demanding high reliability and performance under deployment conditions, directly transferable to ensuring robotics can adapt and perform across diverse environments.

I am adept at designing and integrating state machines and developing frameworks for real-time decision-making, as showcased in my Dobot Magician project where an LLM orchestrated perception and actuation with robust error recovery. My work also involved mentoring and guiding teams on technical excellence and ensuring seamless software-hardware integration. I am confident in my ability to lead critical parts of your robot software stack, mentor a growing team of roboticists, and significantly impact how your robots think, act, and learn in the field. I am excited by the prospect of contributing to a venture-backed AgTech startup and helping scale a technically ambitious company from its seed stage.

Thank you for considering my application. I am available for an interview at your earliest convenience to discuss how my skills and experience can benefit Demeter Robotics.

Sincerely,\\
SHIVAM SHARMA

\end{document}
